Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-24 main.tex
:pencil: Add conclusion

	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \SI{1}{\meter}.
	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[User Coverage\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_frequency.tex}
				}
			}
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\caption{Average primary-(total-)backscatter rate regions.}
			\label{fi:region_config_2}
		\end{figure}
	\end{subsection}
	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.8\columnwidth}{!}{
	% 		\input{assets/simulation/distribution_weights.tex}
	% 	}
	% 	\caption{1}
	% 	% \caption{Average primary-(total-)backscatter rate region.}
	% \end{figure}
	% \begin{table}[t!]
	% 	\centering
	% 	\caption{Parameters in simulation}
	% 	\begin{tabular}{ll}
	% 		Transmit antenna $Q$     & 1   \\
	% 		Tags $K$                 & 2   \\
	% 		States $M$               & 2   \\
	% 		Reflect ratio $\alpha$   & 0.5 \\
	% 		Duration ratio $N$       & 10  \\
	% 		Noise power $\sigma_v^2$ & 1   \\
	% 		Discretization bins      & 256
	% 	\end{tabular}
	% 	\label{ta:parameters}
	% \end{table}
	% Table \ref{ta:parameters} shows the parameters used in simulation.
	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.

	% Figs. \ref{fi:rate_region_1} and \ref{fi:rate_region_2} show two typical scenarios where joint encoding can be helpful and unnecessary, respectively.
	% Although the proposed \gls{kkt} input design converges to the optimal solutions in both examples, it may be trapped at saddle points under poor initialization, especially when the number of tags increases.

	% We believed threshold design has no impact on the primary achievable rate, because primary decoding acts on $\boldsymbol{y}$ while thresholding acts on $z$.
	% As such, the threshold that maximizes the total backscatter rate should also maximize the weighted sum rate.
	% Interestingly, this may not be the case because the \gls{smawk} and Bisection threshold designs, both maximizing the total backscatter rate, can be outperformed by the \gls{ml} when it comes to weighted sum primary-(total-)backscatter rate.
	% It may result from a precision issue, but inspires further research on threshold design for Metascatter.

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{\columnwidth}{!}{
	% 		\includegraphics{assets/illustration/rate_region_1.eps}
	% 	}
	% 	\caption{Achievable rate regions by input-threshold design: Case I.}
	% 	\label{fi:rate_region_1}
	% \end{figure}

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{\columnwidth}{!}{
	% 		\includegraphics{assets/illustration/rate_region_2.eps}
	% 	}
	% 	\caption{Achievable rate regions by input-threshold design: Case II.}
	% 	\label{fi:rate_region_2}
	% \end{figure}
	% The parameters remain fixed unless specified.
\end{section}

>>>>

	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Node Coverage\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_frequency.tex}
				}
			}
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\caption{Average primary-(total-)backscatter rate regions.}
			\label{fi:region_config_2}
		\end{figure}

		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
		Under the assumption of ideal backscatter decoding and re-encoding, Fig. \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and Metascatters boil down to conventional \gls{irs} elements with fixed reflection patterns during whole channel block.
		In Fig. \subref*{fi:region_frequency}, we observe that passive Metascatter achieves higher backscatter rate at lower carrier frequency because of preferable propagation loss.
		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper introduced Metascatter that adapts input distribution of passive backscatter nodes to simultaneously transmit and assist over existing wireless systems.
	Starting from backscatter principles, we showed how Metascatters bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To characterize achievable primary-backscatter rate region, we proposed a \gls{bcd} algorithm that evaluates \gls{kkt} input distribution in closed form, optimizes active beamforming by \gls{pgd}, and refines decision regions by existing methods.
	Numerical results demonstrated the advantage of adaptive node input distribution design for both primary and backscatter subsystems.

	One particular interesting question is how to design Metascatters in a multi-user system.
	If one node can contribute to and be decoded by multiple users, its input distribution may be further adjusted to mimic multi-beam gain of dynamic beamforming \cite{Qiu2022}.
\end{section}
